\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-23 doc/sui14/abstract.tex
created sui2014 dir

%% Yang suggests: Interacting with smart objects in the physical space efficiently is a realistic challenge as these objects become ubiquitous. In this paper, we contribute HOBS, a set of novel methods for selecting physical objects at a distance using infrared-sensed head orientations. We augment a commercial head-worn device, Google Glass, with an infrared (IR) emitter to select targets equipped with IR receivers. We present the iterative design process of our methods, involving a series of interaction technique and hardware design and user evaluations....
Emerging head-worn computing devices can enable interactions with smart objects in physical spaces. 
%
We present the iterative design and evaluation of \systemname -- a head-orientation based selection method for interacting with these devices at a distance. We augment a commercial wearable device, Google Glass, with an infrared (IR) emitter to select targets equipped with IR receivers. Our first design shows that a naive IR implementation can outperform list selection, but has poor performance when refinement between multiple targets is needed. A second design uses IR intensity measurement at targets to improve refinement. To address the lack of natural mapping of on-screen target lists to spatial target location, our third design infers a spatial data structure of the targets from demonstration enabling a natural head-motion based disambiguation.
%
Finally, we demonstrate a universal remote control application using HOBS and report qualitative user impressions.

>>>>

%% Yang suggests: Interacting with smart objects in the physical space efficiently is a realistic challenge as these objects become ubiquitous. In this paper, we contribute HOBS, a set of novel methods for selecting physical objects at a distance using infrared-sensed head orientations. We augment a commercial head-worn device, Google Glass, with an infrared (IR) emitter to select targets equipped with IR receivers. We present the iterative design process of our methods, involving a series of interaction technique and hardware design and user evaluations....
Emerging head-worn computing devices can enable interactions with smart objects in physical spaces. 
%
We present the iterative design and evaluation of \systemname -- a head-orientation based selection method for interacting with these devices at a distance. We augment a commercial wearable device, Google Glass, with an infrared (IR) emitter to select targets equipped with IR receivers. Our first design shows that a naive IR implementation can outperform list selection, but has poor performance when refinement between multiple targets is needed. A second design uses IR intensity measurement at targets to improve refinement. To address the lack of natural mapping of on-screen target lists to spatial target location, our third design infers a spatial data structure of the targets enabling a natural head-motion based disambiguation.
%
Finally, we demonstrate a universal remote control application using HOBS and report qualitative user impressions.

### 2014-06-23 doc/sui14/applications.tex
created sui2014 dir

We implemented a prototype of this remote controller for three physical devices: a lamp and fan that could be switched on or off; and a smart TV control with playback, volume and navigation controls (see Figure~\ref{fig:smart-home}). We switched discrete appliances using relays, and implemented the smart TV with a laptop connected to a 30\inch{} display. User interfaces for each were pre-defined in our application.

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/smarthome-scenario.pdf}
\caption{In the smart home scenario, we have built three smart appliances for a user experience study. The control interface supports both simple on/off appliances (lamp or fan) and multi-functional appliances (TV, for example).}
\label{fig:smart-home}
\end{figure}

>>>>

We implemented a prototype of this remote controller for three physical devices: a lamp and fan that could be switched on or off, and a smart TV control with playback, volume and navigation controls (see Figure~\ref{fig:smart-home}). We switched discrete appliances using relays, and implemented the smart TV with a laptop connected to a 30\inch{} display. User interfaces for each were pre-defined in our application.

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/smarthome-scenario.pdf}
\caption{In the smart home scenario, we have built three smart appliances for a user experience study. The interface supports both simple on/off appliances (lamp or fan) and multi-functional appliances (TV, for example).}
\label{fig:smart-home}
\end{figure}

### 2014-06-23 doc/sui14/disambiguation.tex
created sui2014 dir

For area selection technique, when multiple targets are within the range, the disambiguation is necessary. We propose three different ways of disambiguation solutions in this section. Initially our system leaves the disambiguation to the user \ben{cite our paper}. However, our studies showed that manual disambiguation is a time-consuming task, so we only consult manual action when the system cannot figure out itself. The automatic disambiguation are based on the observation that users tend to adjust their head orientation a bit when they found the target is wrong. So we achieve a more fine-grained targeting by exploiting the IR intensity and the change of IR readings, as well as the sensors on Google Glass.

>>>>

In our previous section we have described how we design and choose the COTS components for our prototype. However, for area selection technique, when multiple targets are within the range, the disambiguation is necessary. We could just leave this as a manual operation to the user; however, from previous studies \cite{Chen:EECS-2013-200} we have found that this becomes the bottleneck for seamless interaction in many cases. Therefore, we consider the problem of simplifying disambiguation in physical targeting contexts by incorporating multiple sources of sensors.

The first and most straightforward way is to use the signal strength of area selection technique. For IR, we have added IR light-to-voltage converter to read the absolute IR intensity. The second class of sensors are those available on wearable devices. Google Glass' motion sensors are the ones that we have used in our study. The automatic disambiguation will definitely save time, but leaving the option of manual switching targets will still be useful. But this doesn't necessarily mean the naive list browsing technique. We consider how the IR and motion sensors can helps us build a smarter list -- adjacent map -- when manual switching is performed. We talk about each technique in the following few subsections.

### 2014-06-23 doc/sui14/intro.tex
created sui2014 dir

In response, we designed an improved refinement technique, {\em Intensity IR}, in which target objects compare received IR signal strength. This value allows the system to eliminate some distracting targets on the peripheral and to re-order the refinement interface's list by their intensity values. For example, in Figure~\ref{fig:teaser}B of {\em Intensity IR} technique, device 5 is eliminated first and the list is re-ordered based on the intensity readings. A second study with $10$ participants proves that {\em Intensity IR} successfully reduces both the chance of needing to do refinement as well as the time spent in list navigation when compared to {\em Naive IR}.

>>>>

In response, we designed an improved refinement technique, {\em Intensity IR}, in which target objects compare received IR signal strength. This value allows the system to eliminate some distracting targets on the peripheral and to re-order the refinement interface's list by their intensity values. For example, in Figure~\ref{fig:teaser} of {\em Intensity IR} technique, device 5 is eliminated first and the list is re-ordered based on the intensity readings. A second study with $10$ participants proves that {\em Intensity IR} successfully reduces both the chance of needing to do refinement as well as the time spent in list navigation when compared to {\em Naive IR}.

### 2014-06-23 doc/sui14/sui14.tex
created sui2014 dir

%% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
%% \toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org.}
% {\emph{CHI'14}}, April 26--May 1, 2014, Toronto, Canada. \\
% Copyright \copyright~2014 ACM ISBN/14/04...\$15.00. \\
% DOI string from ACM form confirmation}
%% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)

\toappear{}
%Submitted to CHI2014. Do not cite or distribute without written permission from the authors.}

@@

% Load basic packages
\usepackage{balance}  % to better equalize the last page
\usepackage{graphics} % for EPS, load graphicx instead
\usepackage{times}    % comment if you want LaTeX's default font
\usepackage{url}      % llt: nicely formatted URLs
\usepackage{gensymb}
\usepackage{afterpage}
% see http://tex.stackexchange.com/questions/46055/typesetting-with-inch-symbols-and-sizes-in-inches
\usepackage{mathpazo,amsmath}
\def\inch#1{#1''}
\def\ft#1{#1'\thinspace}

% llt: Define a global style for URLs, rather that the default one
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\bf\ttfamily}}}
\makeatother
\urlstyle{leo}

@@

%use these commands while writing
\newcommand {\bjoern}[1]{{\color{red}\bf{BH: #1}\normalfont}}
\newcommand {\ben}[1]{{\color{blue}\bf{BZ: #1}\normalfont}}
\newcommand {\sean}[1]{{\color{blue}\bf{SC: #1}\normalfont}}
\newcommand {\claire}[1]{{\color{blue}\bf{CT: #1}\normalfont}}
\newcommand {\studyquote}[1]{\em ``#1''\normalfont}
%comment out the above and uncomment these for final submit
%\newcommand {\bjoern}[1]{}
%\newcommand {\ben}[1]{}
%\newcommand {\sean}[1]{}
%\newcommand {\claire}[1]{}

@@

\title{A Context Menu for the Real World: Controlling Physical Appliances Through Head-Worn Infrared Targeting}

\numberofauthors{1}
\author{
\alignauthor Yu-Hsiang Chen$^{\dagger}$, Ben Zhang$^{\dagger}$, Claire Tuna$^{\dagger}$, Yang Li$^{\ddagger}$, Edward Lee$^{\dagger}$, Bj\"orn Hartmann$^{\dagger}$ \\
\affaddr{$\dagger$: UC Berkeley EECS \& CITRIS Invention Lab \hspace{0.25in} $\ddagger$: Google Research}\\
\email{sean.yhc@gmail.com, benzh@eecs.berkeley.edu, clairetuna@gmail.com, yangli@acm.org, eal@eecs.berkeley.edu, bjoern@eecs.berkeley.edu}
}
%\author{
% \alignauthor Anonymous for submission
%  \alignauthor 3rd Author Name\\
%    \affaddr{Affiliation}\\
%    \affaddr{Address}\\
%    \email{e-mail address}\\
%    \affaddr{Optional phone number}

@@

\begin{abstract}
\input{abstract}
\end{abstract}

\keywords{
	smart devices; universal remote control; wearable computing; glass
}

\category{H.5.m.}{Information Interfaces and Presentation (e.g. HCI)}{Miscellaneous}

%$See: \url{http://www.acm.org/about/class/1998/}
%for more information and the full list of ACM classifiers
%and descriptors. 
%\textcolor{red}{Mandatory section to be included in your
%final version. On the submission page only the classifiers'
%letter-number combination will need to be entered.}

\input{introduction}
\input{relatedwork}
\input{interaction}
\input{device}
\input{targeting}
\input{control}
\input{discussion}
\input{conclusion}
\section{Acknowledgments}
This work was supported in part by the TerraSwarm Research Center, one of six centers supported by the STARnet phase of the Focus Center Research Program (FCRP) a Semiconductor Research Corporation program sponsored by MARCO and DARPA. Additional support was provided by a Sloan Foundation Fellowship and a Google Research Award.

%figure template:
%\begin{figure}[!h]
%\centering
%\includegraphics[width=1.0\columnwidth]{Figure1}
%\caption{With Caption Below, be sure to have a good resolution image
%  (see item D within the preparation instructions).}
%\label{fig:figure1}
%\end{figure}

% Balancing columns in a ref list is a bit of a pain because you
% either use a hack like flushend or balance, or manually insert
% a column break.  http://www.tex.ac.uk/cgi-bin/texfaq2html?label=balance
% multicols doesn't work because we're already in two-column mode,
% and flushend isn't awesome, so I choose balance.  See this
% for more info: http://cs.brown.edu/system/software/latex/doc/balance.pdf
%
% Note that in a perfect world balance wants to be in the first
% column of the last page.
%
% If balance doesn't work for you, you can remove that and
% hard-code a column break into the bbl file right before you
% submit:
%
% http://stackoverflow.com/questions/2149854/how-to-manually-equalize-columns-
% in-an-ieee-paper-if-using-bibtex
%
% Or, just remove \balance and give up on balancing the last page.
%
\balance

% REFERENCES FORMAT
% References must be the same font size as other body text.

\bibliographystyle{acm-sigchi}
\bibliography{sigchi14}
\end{document}

>>>>

%% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
% \toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is 	granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org. \\\textbf{}
% {\emph{CHI'14}}, April 26--May 1, 2014, Toronto, Canada. \\
% Copyright \copyright~2014 ACM ISBN/14/04...\$15.00. \\
% DOI string from ACM form confirmation}
%% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
\toappear{Submitted for review to SUI 2014.}

@@

% Load basic packages
\usepackage{balance}  % to better equalize the last page
\usepackage{graphics} % for EPS, load graphicx instead
\usepackage{times}    % comment if you want LaTeX's default font
\usepackage{url}      % llt: nicely formatted URLs
% llt: Define a global style for URLs, rather that the default one
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\bf\ttfamily}}}
\makeatother
\urlstyle{leo}

\usepackage{gensymb}
\usepackage{afterpage}
% see http://tex.stackexchange.com/questions/46055/typesetting-with-inch-symbols-and-sizes-in-inches
% \usepackage{mathpazo}
\usepackage{amsmath}
\def\inch#1{#1''}
\def\ft#1{#1'\thinspace}

% comment macros are in inputmacros.tex
\input{inputmacros}

@@

@@

% as we discussed last time, the "Sees" and "Line-of-sight" suggests some computer vision direction 
% need a different title for sure, but not in a hurry
\title{\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces}
%Project GlasSees: Direct Interaction Through Line-of-sight}

\iftoggle{anonymous}{
\author{
 \alignauthor Anonymous for submission\\
    %\affaddr{...}\\
    %\email{...}\\
  }
}{ %else
  \numberofauthors{1}
  \author{
  \alignauthor  Ben Zhang$^{\dagger}$, Yu-Hsiang Chen$^{\dagger}$, Claire Tuna$^{\dagger}$, Achal Dave$^{\dagger}$,\\Yang Li$^{\ddagger}$, Edward Lee$^{\dagger}$, Bj\"orn Hartmann$^{\dagger}$ \\
  \affaddr{$\dagger$: UC Berkeley EECS \& CITRIS Invention Lab \hspace{0.25in} $\ddagger$: Google Research}\\
  \email{\{benzh,clairetuna,achal,eal,bjoern\}@berkeley.edu, sean.yhc@gmail.com, yangli@acm.org}
  }
}

\teaser{
  \centering
  \includegraphics[width=\textwidth]{figures/teaser.png}
  \caption{{\em Left}: Our head orientation-based selection techniques use an IR emitter -- multiple targets may fall within its illumination area. {\em Center}: We offer two list-based refinement techniques -- {\em Naive IR} uses alphabetical ordering; {\em Intensity IR} orders targets by IR intensity. {\em Right}: Alternatively, users can refine their selection through head orientation refinement in a quasi-mode.}
  \label{fig:teaser}
}

%% the third part of the teaser: An example application of head-orientation targeting: Using an augmented head-worn device (1), users can control smart home appliances (2) by looking at them. A near-eye display then shows an appliance control UI (3), which users navigate through multitouch gestures.}

@@

\begin{abstract}
\input{abstract}
\end{abstract}
\vspace{-0.05in}
\keywords{
  Wearable computing; selection; glass; infrared
}
\vspace{-0.1in}
%% refer to http://www.acm.org/about/class/ccs98-html
\category{H.5.2.}{Information Interfaces and Presentation (e.g. HCI)}{Interaction styles (e.g., commands, menus, forms, direct manipulation).}

\input{intro}
\input{relatedwork}
\input{interaction}
\input{iteration1}
\input{iteration2}
\input{iteration3}
%\input{disambiguation}
%\input{evaluation}

%% the rest of the paper seems to be fine; it's mainly the texts
\input{applications}
\input{discussion}
\input{conclusion}

\iftoggle{anonymous}{
% no acks in anonymous submission
}{
  \section{Acknowledgments}

  This work was supported in part by the TerraSwarm Research Center, one of six centers supported by the STARnet phase of the Focus Center Research Program (FCRP) a Semiconductor Research Corporation program sponsored by MARCO and DARPA. Additional support was provided by a Sloan Foundation Fellowship and a Google Research Award.
}
%figure template:
%\begin{figure}[!h]
%\centering
%\includegraphics[width=1.0\columnwidth]{Figure1}
%\caption{With Caption Below, be sure to have a good resolution image
%  (see item D within the preparation instructions).}
%\label{fig:figure1}
%\end{figure}

% Balancing columns in a ref list is a bit of a pain because you
% either use a hack like flushend or balance, or manually insert
% a column break.  http://www.tex.ac.uk/cgi-bin/texfaq2html?label=balance
% multicols doesn't work because we're already in two-column mode,
% and flushend isn't awesome, so I choose balance.  See this
% for more info: http://cs.brown.edu/system/software/latex/doc/balance.pdf
%
% Note that in a perfect world balance wants to be in the first
% column of the last page.
%
% If balance doesn't work for you, you can remove that and
% hard-code a column break into the bbl file right before you
% submit:
%
% http://stackoverflow.com/questions/2149854/how-to-manually-equalize-columns-
% in-an-ieee-paper-if-using-bibtex
%
% Or, just remove \balance and give up on balancing the last page.
%
%% \balance

\bibliographystyle{acm-sigchi}
\bibliography{sui14}
\end{document}
